Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-11 popl24/proofs.tex
Update proofs.tex

\begin{proof}
  By assumptions of well-typedness we have:
  $$
  \begin{array}{rcl}
    v &=&  \ttt{\{shares1 = }v_1\ttt{; shares2 = }v_2\ttt{\}}\\
    v_1 &=& \ttt{\{ c1 = v[1,s1out]; c2 = v[2,s1out] \}}\\
    v_2 &=& \ttt{\{ c1 = v[1,s2out]; c2 = v[2,s2out] \}}
  \end{array}
  $$
  And by Definition \ref{definition-gmwencode-certification} we have:
  \begin{mathpar}
    \sep{\progtt(\prog)}{\ttt{\{s[1,s1]\}}}{\ttt{\{v[2,s1out],v[2,s2out]\}}}

    \sep{\progtt(\prog)}{\ttt{\{s[2,s2]\}}}{\ttt{\{v[1,s1out],v[1,s2out]\}}}
  \end{mathpar}
  Since we assume that secrets are in uniform and independent marginal
  distributions a priori, and $\vars(\prog_1) \cap \vars(\prog_2) =
  \varnothing$ by condition (iii) of Definition 
  \ref{definition-gmwencode-certification} and assumptions of well-typedness, 
  the result follows by preconditions and Lemma \ref{lemma-separation}.
\end{proof}

@@

\begin{proof}
  By Definition \ref{definition-ygcencode-certification} we have:
  \begin{mathpar}
    \sep{\progtt(\prog_2)}{\ttt{\{s[1,s1]\}}}{\vdefs(\prog_2)_{\{2\}}}

    \sep{\progtt(\prog_2)}{\ttt{\{s[2,s2]\}}}{\vdefs(\prog_2)_{\{1\}}}
  \end{mathpar}
  Since we assume that secrets are in uniform and independent marginal
  distributions a priori, and $\vars(\prog_1) \cap \vars(\prog_2) =
  \varnothing$ by condition (iv) of Definition
  \ref{definition-ygcencode-certification} and assumptions of
  well-typedness, conditions (ii-iii) follow by Lemmas
  \ref{lemma-noninterference} and \ref{lemma-separation}. Also by
  Definition \ref{definition-ygcencode-certification} we have
  $\gc{\prog_2}{v_1}{s_1}$ and $\gc{\prog_2}{v_1}{s_1}$, so also
  $\gc{\prog_1;\prog_2}{v_1}{s_1}$ and
  $\gc{\prog_1;\prog_2}{v_1}{s_1}$ by condition (iv) of Definition
  \ref{definition-ygcencode-certification} and Lemmas
  \ref{lemma-noninterference} and \ref{lemma-separation}.
\end{proof}

>>>>

\begin{proof}
  By assumptions of well-typedness we have:
  $$
  \begin{array}{rcl}
    v &=&  \ttt{\{shares1 = }v_1\ttt{; shares2 = }v_2\ttt{\}}\\
    v_1 &=& \ttt{\{ c1 = v[1,"s1out"]; c2 = v[2,"s1out"] \}}\\
    v_2 &=& \ttt{\{ c1 = v[1,"s2out"]; c2 = v[2,"s2out"] \}}
  \end{array}
  $$
  And by Definition \ref{definition-gmwencode-certification} we have:
  \begin{mathpar}
    \sep{\progtt(\prog)}{\ttt{\{s[1,"s1"]\}}}{\ttt{\{v[2,"s1out"],v[2,"s2out"]\}}}

    \sep{\progtt(\prog)}{\ttt{\{s[2,"s2"]\}}}{\ttt{\{v[1,"s1out"],v[1,"s2out"]\}}}
  \end{mathpar}
  Since we assume that secrets are in uniform and independent marginal
  distributions a priori, and $\vars(\prog_1) \cap \vars(\prog_2) =
  \varnothing$ by condition (iii) of Definition 
  \ref{definition-gmwencode-certification} and assumptions of well-typedness, 
  the result follows by preconditions and Lemma \ref{lemma-separation}.
\end{proof}

@@

\begin{proof}
  By Definition \ref{definition-ygcencode-certification} we have:
  \begin{mathpar}
    \sep{\progtt(\prog_2)}{\ttt{\{s[1,"s1"]\}}}{\vdefs(\prog_2)_{\{2\}}}

    \sep{\progtt(\prog_2)}{\ttt{\{s[2,"s2"]\}}}{\vdefs(\prog_2)_{\{1\}}}
  \end{mathpar}
  Since we assume that secrets are in uniform and independent marginal
  distributions a priori, and $\vars(\prog_1) \cap \vars(\prog_2) =
  \varnothing$ by condition (iv) of Definition
  \ref{definition-ygcencode-certification} and assumptions of
  well-typedness, conditions (ii-iii) follow by Lemmas
  \ref{lemma-noninterference} and \ref{lemma-separation}. Also by
  Definition \ref{definition-ygcencode-certification} we have
  $\gc{\prog_2}{v_1}{s_1}$ and $\gc{\prog_2}{v_1}{s_1}$, so also
  $\gc{\prog_1;\prog_2}{v_1}{s_1}$ and
  $\gc{\prog_1;\prog_2}{v_1}{s_1}$ by condition (iv) of Definition
  \ref{definition-ygcencode-certification} and Lemmas
  \ref{lemma-noninterference} and \ref{lemma-separation}.
\end{proof}
